External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising

### 2016-10-15 egpaper_for_review.tex
a

>>>>

\subsection{Discussion on Parameter $\lambda$}
The proposed method only has a key parameter, namely the regularization paramters $\lambda$. To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$. The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.2dB (0.9620) when $\lambda$ varies from $1e-3$ to $4e-4$. This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
\begin{figure}
\includegraphics[width=1\linewidth]{images/param.png}
\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
\label{fig10}
\end{figure}
